---
title: "CDS9W4"
author: "Pascal Bellerose"
date: "September 25, 2017"
output: slidy_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary

 - This presentation is part of the assignment for course Developing Data Products, week 4, on Coursera.org.

 - The presentation was generated using ***RStudio***(<https://www.rstudio.com>) and ***Slidify***(<http://slidify.org>) framework.

## Application

 - The second half of the mentioned assignment was to develop a web application. The application was named **Milleage per Gallon Determination**.
 

 - This application shows an example of making a web application using R and [Shiny](https://shiny.rstudio.com) framework together.
 
 - In the application, a prediction model is generated, based on a car parameters dataset (HP, weight, gears, etc.). Then, a user can play freely with the UI values in order to simulate the parameters of an hypothetical car and be able to predict its MPG consumption.
 
 - The application and the current presentation source codes can be found at <https://github.com/FireFighter1017/CDS9W4>. The application comprises 3 files: *ui.R* (UI), *server.R* (backend) and *modelBuilding.R* (Random Forest predictor).
  
## Dataset

Dataset used by the application is the [Motor Trend Car Road Tests](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html) (from now on *'mtcars'*). The data was extracted from the ***1974 Motor Trend*** US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

Next, the dataset structure: 
```{r cars, echo = TRUE}
str(mtcars)
```

## Prediction

A Random Forest prediction model is generated and trained using the *'mtcars'* dataset. The goal of this model is to predict the fuel consumption (***mpg*** variable) based on the rest of the variables:
```{r echo = FALSE, warning=FALSE, message=FALSE}
library(caret)
library(randomForest)

set.seed(030508)

```

```{r echo = TRUE, eval=FALSE}
customTrainControl <- trainControl(method = "cv", number = 10)
carsRandomForestModelBuilder <- function() {
  return(
    train(
      mpg ~ ., 
      data = mtcars,
      method = "rf",
      trControl = customTrainControl
    )
  )
}

carsRandomForestModelBuilder()
```
